---
title: "Assignment 2 BusAna"
author: "1st markdown"
date: "3/7/2021"
output: html_document
---

```{r}
install.packages('mlbench')
library(mlbench)
data(BostonHousing)

```


```{r}
set.seed(2017)
X=runif(100)*10
Y=X*4+3.45
Y=rnorm(100)*0.29*Y+Y

```

1a.
```{r}
plot(X,Y)
```
Yes we can definitely fit a linear model on this graph

1b.
```{r}
Modco=lm(Y ~X)

Modco$coefficients
```
Y = 4.465490X + B3.610759  

```{r}
Accuracy<-3.610759/4.465490
Accuracy
```
1c.
With a predictor of 81% that means that the x variable predicts the Y intercept 81% of the time accurately. 


2a
```{r}
Mtcars<-data("mtcars")
```

```{r}
View(mtcars)
```

```{r}
James <- lm(mtcars$wt ~mtcars$hp)
```

```{r}
James
```
```{r}
.009401/1.838247
```
James is more accurate

```{r}
Chris<- lm(mtcars$mpg ~ mtcars$hp)
Chris
```
```{r}
MPG<--.06823/30.09886
MPG
```


2b.
```{r}
lm(hp ~cyl + mpg, data = mtcars)
```

```{r}
PredictedHP <- 54.067 + (23.979 *4) + (-.2775 * 22)
```

```{r}
PredictedHP
```

3a.
```{r}
ArgPrice<-lm( formula = medv~ crim + chas + ptratio +  zn, data = BostonHousing)
ArgPrice
```
```{r}
summary(ArgPrice)
```
With a R-Squared of 36% this doesn't seem to be a good model in terms of accuracy

3b 1
```{r}
Chas1 <- lm(medv ~ chas == 1, data = BostonHousing)
chas2 <- lm(medv ~ chas == 0, data = BostonHousing)
```


```{r}
Chas1

chas2
```
Price not next to river = 22.094
Price next to river = 28.44

```{r}
Pricedifference <- 28.44 - 22.094
Pricedifference
```
The differences align in the method I used above and the regression modeling below
```{r}
Chasreg <- lm(medv ~ chas, data = BostonHousing)
summary(Chasreg)
```


```{r}
summary(ArgPrice)
```
With a Multiple R-Squared value of .3599 that is stating that only 35% of the median value can be explained by the crime crate, proportion of residential land zoned for lots over 25000 sqft., local pupil-teacher ratio, and whether the tract bounds the Chas River. Making this a pretty poor model in terms of accuracy.
```{r}

lm(medv~chas, data = BostonHousing)
```

3c.
The chas river is the significant value in determining the housing price.P-Value of 0.000514

3D.
```{r}
anova(ArgPrice)
```
Importance order is
1. ptratio
2. crim
3. chas
4. zn


