---
title: "Quant 5 HW"
author: "Devante Lee1"
date: "11/1/2020"
output: html_document
---
Objective function: 
20x1 + 15x2 + 25x3 + 6yic + -6yic + -3yid

Mathematical objective

Maximize 20x1 + 15x2 + 25x3 + 6yic + -6yic + -3yid
          Y1 + - y1- = 6x1 + 4x2+ 5x3 – 50
          -Y2 - = 8x2 + 7x2 + 5x3 – 75
          
Final Formulation
Maximize Z = 20x1 + 15x2 + 25x3 + 6yic + -6yic + -3yid
 6x1 + 4x2+ 5x3 -(Y1 + - y1-) = 50
 8x1 + 7x2 + 5x3 -(-y2) >= 75


```{r}
library(lpSolveAPI)
```

```{r}
HW5 <- make.lp(,6)
```

```{r}
set.objfn(HW5, c(20, 15, 25, 6, -6, -3))

```

```{r}
lp.control(HW5, sense = "max")
```


```{r}
x1 <- c(6, 4, 5, 1, 1, 0 )
add.constraint(HW5, x1, type = "=", 50)
```

```{r}
x2 <- c(8, 7, 5, 0, 0, 1)
add.constraint(HW5, x2, type = ">=", 75)
```
```{r}
solve(HW5)
get.objective(HW5)
get.variables(HW5)
```
We will be able to get our total profit to 208,000,000.
In conclusion it seems that the first goal is completley satisfied. The second goal however is not satisfied which resulted in a penalty for exceeding this goal by 833. The penalty for exceeding this goal is 33.33.
